The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-11-12 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

Tests for differences in proportions were conducted for comparing winning percentage
and the three different shooting percentages in 2020 to those of
2017-2019. The null hypothesis is 
\[
H_0: p_1 = p_2,
\]
where $p_1$ and $p_2$ are the shooting percentage in 2020 and
2017-2019, respectively. Let
$\hat{p}_1$ represents sample proportion for 2020 and $\hat{p}_2$ represents sample
proportion for 2017-2019. The test statistic is
\begin{align}
    z = \frac{\hat{p}_1 - \hat{p}_2}{\sqrt{\hat{p}(1-\hat{p})(\frac{1}{n_1}+\frac{1}{n_2})}},
    (\#eq:zprop)
\end{align}
where $\hat p$ is the pooled shooting percentage of 2017-2020.
The null distribution of the test statistic is also standard normal
The test will be conducted seven times,once comparing home winning percentage for 
2020 to that of 2017-2019 and once for each oftwo-point shooting, three-point shooting and
free throws for both home and away teams in 2020 vs. 2017-2019. Again these tests will
run simultaneously as a z-test and a Wilcoxon test.

>>>>

Tests for differences in proportions were conducted for comparing winning percentage
and the three different shooting percentages in 2020 to those of
2017-2019. The null hypothesis is 
\[
H_0: p_1 = p_2,
\]
where $p_1$ and $p_2$ are the shooting percentage in 2020 and
2017-2019, respectively. Let
$\hat{p}_1$ represents sample proportion for 2020 and $\hat{p}_2$ represents sample
proportion for 2017-2019. The test statistic is
where $\hat p$ is the pooled shooting percentage of 2017-2020.
The null distribution of the test statistic is also standard normal.
The test will be conducted seven times, once comparing home winning percentage for 
2020 to that of 2017-2019 and once for each of two-point shooting, three-point shooting and
free throws for both home and away teams in 2020 vs. 2017-2019. Again these tests will
run simultaneously as a z-test and a Wilcoxon test.
